Stats

### 2023-05-12 paper/manuscript.Rmd
incorporate reviews round 2

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test–retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya].
The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities [e.g., @wellman2004scaling], and which factors drive the development of social cognition [e.g., @gola2012mental; @devine2018family].
For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development [@okumura2017individual].
In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @poulin-dubois2023discontinuity; @sodian2023reply; @sodian2016understanding].
This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
As such, the eyes have been regarded as a "window into the mind" [@shepherd2010following].
Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions [@tomasello2007reliance; @bohn2018common].
In addition, gaze and language development seem to be related [@brooks2005development].
Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication [@macdonald2013eye; @hernik2019infant].
While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
However, many cognitive abilities continue to develop beyond early childhood [e.g., @gathercole2004structure for working memory; @raviv2018developmental for visual statistical learning].
Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
Consequently, we aimed to assess the differentiation of the ability to understand gaze.
Our goal was not to establish the youngest age at which children understand gaze cues.
Rather, we wanted to examine how that ability changes with age.
To accurately measure developmental change, we were interested in capturing individual variability.

@@

Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.

@@

Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
They often live in nuclear two-generational families with few household members.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
The median individual monthly net income in the year 2021 was \~ 1,600€ for the city of Leipzig.

@@

For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.

@@

(ref:figlab2) **Measuring inter-individual variation**. (A) Developmental trajectory in the continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in the discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. The dotted black line shows the level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode. For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*. Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection. The color of data points denotes age group.

@@

Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1; manifested in too early clicking in the training trials while the instructions were still playing, and no clicking by themselves in the test trials).
Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.

The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).
Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).

@@

We assessed reliability in two ways.
First, we focused on internal consistency by calculating split-half reliability coefficients.[^3]
For each subject, trials were split into odd and even trials.
Performance was aggregated and then correlated using *Pearson* coefficients.
For this, we used the data of the first test day.
Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.

@@

After having probed our new testing infrastructure and the psychometric properties of the TANGO task, we aimed at establishing its validity. 
One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related. 
Social cognition is often described as developing in response to social interaction [@devine2018family; @hughes2004links]. 
It is assumed that opportunities to play, communicate and argue with peers help children to understand the human mind.
Therefore, many studies link social cognition to opportunities for social interaction captured in demographic variables such as parent-child interaction quality and quantity, mental state talk, and center-based childcare [@bulgarelli2016social; @pavarini2013parental; @dunn1991young].
In particular, family constellation, the number and age of siblings, and their interaction have been linked to social cognition [@zhang2021worse; @cassidy2005theory; @perner1994theory; @peterson2000kindred; @dunn1991young].

To assess such external validity for the TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day. 
`r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers. 
Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements). Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see Supplements for distribution characteristics of the predictors). Albeit the effects were weak, they are consistent with the literature.

In addition, children's sensitivity to gaze has been linked to language acquisition [@brooks2005development; @okumura2017individual; @delbianco2019developmental].
Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [@bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO task. 
We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)B and C).
Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic of measures of social cognition.

(ref:figlab4) **Validity of the TANGO task.** (A) Influence of age of childcare entry on gaze understanding. The older the children were when entering childcare, the less likely they are to respond correctly. (B) Influence of social-environmental factors on gaze understanding. Adding each predictors respectively to the null model did not improve model fit. (C) Influence of gaze understanding on receptive vocabulary. (D) Influence of gaze understanding on receptive vocabulary by age. The regression line with 95% CI shows a smooth conditional mean based on a linear model, with a *Pearson*’s correlation coefficient *r*. Dots show the mean performance for each subject averaged across trials. The color of dots denotes age group. For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model. Black dots represent means, thicker black lines 80% CI and thinner black lines 95% CI.

@@

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible for use and modification.

@@

Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
Both study versions exhibit high retest reliability, also when controlling for age.
Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).

@@

With respect to validity, we found that performance in the TANGO task was related to relevant external variables and cognitive measures.
Family-level variables, capturing a child’s opportunity for social interaction, systematically influenced gaze understanding. Even though the effects were small and confidence intervals were wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real-life variables. 
In addition, we assessed the influence of gaze understanding on receptive vocabulary. 
We found a substantial relationship between the two variables, even when correcting for age. 
Taken together, this speaks to the validity of our TANGO task.

@@

First, we want to address the scope and interpretation of the TANGO task.
We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
This speaks to the face validity of the TANGO task and its focus on an inherently social stimulus.
However, we do not want to claim that the TANGO task does not also recruit other, domain general processes.
For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
From that perspective, gaze understanding could be seen as a particular case of vector-following that is learned and used in social interactions.
Future research could assess how much variation of the gaze understanding task is shared with a physical vector-following task.
In addition, computational cognitive models might prove helpful in defining children's behavior on a process-level and disentangling parameters that influence task performance (e.g., spatial acuity).

@@

@@

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
The data sets and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
A demo version of the task is available at the following website (see Figure \@ref(fig:fig5)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
The code base and respective assets can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
These resources allow interested researchers to use, extend and adapt the task.

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test–retest reliability estimates underline that the captured variation is systematic. Associations with social-environmental factors and language skills speak toward the validity of the task. This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya].
The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities [e.g., @wellman2004scaling], and which factors drive the development of social cognition [e.g., @gola2012mental; @devine2018family].
For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development [@okumura2017individual].
In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @poulin-dubois2023discontinuity; @sodian2023reply; @sodian2016understanding].
This might be because traditional measures of social cognition are not designed to capture variation *between* children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic, reliable, and valid way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
As such, the eyes have been regarded as a "window into the mind" [@shepherd2010following].
Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions [@tomasello2007reliance; @bohn2018common].
In addition, gaze and language development seem to be related [@brooks2005development].
Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication [@macdonald2013eye; @hernik2019infant].

While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
However, many cognitive abilities continue to develop beyond early childhood [e.g., @gathercole2004structure for working memory; @raviv2018developmental for visual statistical learning].
Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
Consequently, we aimed to assess the differentiation of the ability to understand gaze.
Our goal was *not* to establish the youngest age at which children understand gaze cues.
Rather, we wanted to examine how that ability changes with age.
To accurately measure developmental change, we were interested in capturing individual variability.

@@

Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
Furthermore, we were interested in whether and how the data collection mode (in-person vs. remote) influences responses. Since we expected a greater difference in responses between the two data collection modes for children, the analysis of data collection mode was restricted to a child sample.

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
The additional analyses mentioned in the pre-registrations (e.g., computational model) address separate research questions (e.g., how can we explain the concept and process of gaze understanding?) and will be reported elsewhere. In this paper, we focus on the methodological and psychometric aspects of our task.

@@

Please note that we did not collect participant-specific demographics. 
In the following, we aim to provide context and generalizations based on the broader community and the larger pool of potential participants. 
Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
They often live in nuclear two-generational families with few household members.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
The median individual monthly net income in the year 2021 was \~ 1,600€ for the city of Leipzig.

@@

For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
We inspected the posterior distribution (mean and 95% Credible Interval (CrI)) for the age and data collection estimates.

@@

(ref:figlab2) **Measuring inter-individual variation**. (A) Developmental trajectory in the continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in the discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. The dotted black line shows the level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode. Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. For adult data in (A) and (F), we added minimal horizontal and vertical noise to avoid overplotting. The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection. The color of data points denotes age group. For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.

@@

Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1; manifested in too early clicking in the training trials while the instructions were still playing, and no clicking by themselves in the test trials).
Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
Similar to our first study, we did not collect participant-specific demographics. For a community-based description of our participant pool, see Participant section of the first study.

As in our first study, adults were recruited via *Prolific* [@palan2018prolific].
The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).
Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).
See Supplements and the available online data set for more detailed information.

@@

We assessed reliability in two ways.
First, we focused on internal consistency by calculating split-half reliability coefficients.[^3]
For each subject, trials were split into odd and even trials.
Performance was aggregated and then correlated using *Pearson* correlation coefficients.
For this, we used the data of the first test day.
Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.

@@

After having probed our new testing infrastructure and the psychometric properties of the TANGO, we aimed at establishing its validity. 
One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related. 
Social cognition is often described as developing in response to social interaction [@devine2018family; @hughes2004links]. 
It is assumed that opportunities to play, communicate and argue with peers help children to understand the human mind.
Therefore, many studies link social cognition to opportunities for social interaction captured in demographic variables such as parent-child interaction quality and quantity, mental state talk, and center-based childcare [@bulgarelli2016social; @pavarini2013parental; @dunn1991young].
In particular, family constellation, the number and age of siblings, and their interaction have been linked to social cognition [@zhang2021worse; @cassidy2005theory; @perner1994theory; @peterson2000kindred; @dunn1991young].

To assess such external validity for the TANGO, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day. 
`r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers. 
Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements). Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see Supplements for distribution characteristics of the predictors). Albeit the effects were weak, they are consistent with the literature.

In addition, children's sensitivity to gaze has been linked to language acquisition [@brooks2005development; @okumura2017individual; @delbianco2019developmental].
Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [oREV; @bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO. In the oREV task, children are shown four pictures (target word, distractor with similar age-of-acquisition rating, phonological distractor, and semantic distractor; see Supplements for further detail) and hear a verbal prompt asking them to select one of the pictures. The oREV score then represents the proportion of correctly identified target pictures. We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)C and D).
Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic of measures of social cognition.

(ref:figlab4) **Validity of the TANGO.** (A) Influence of age of childcare entry on gaze understanding. The older the children were when entering childcare, the less likely they are to respond correctly. (B) Influence of social-environmental factors on gaze understanding. Adding each predictors respectively to the null model did not improve model fit. (C) Influence of gaze understanding on receptive vocabulary. The oREV score represents a proportion of correctly identified target words in the receptive vocabulary test. Similarly, the TANGO score refers to proportion of correctly located targets (see Supplements for further detail). (D) Influence of gaze understanding on receptive vocabulary by age. The regression line with 95% CI shows a smooth conditional mean based on a generalized linear model, with *Pearson*’s correlation coefficient *r*. Dots show the mean performance for each subject averaged across trials with minimal horizontal and vertical noise added to avoid overplotting. The color of dots denotes age group. For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model. Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.

@@

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
Second, our task showed satisfactory psychometric properties with respect to internal consistency and test-retest reliability estimates.
Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible for use and modification.

@@

Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
Both study versions exhibit high test-retest reliability, also when controlling for age.
Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).

@@

With respect to validity, we found that performance in the TANGO was related to relevant external variables and cognitive measures.
Family-level variables, capturing a child’s opportunity for social interaction, systematically influenced gaze understanding. Even though the effects were small and confidence intervals were wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real-life variables. 
In addition, we assessed the influence of gaze understanding on receptive vocabulary. 
We found a substantial relationship between the two variables, even when correcting for age. 
Taken together, this speaks to the validity of the TANGO.

@@

First, we want to address the scope and interpretation of the TANGO.
We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
This speaks to the face validity of the TANGO and its focus on an inherently social stimulus.
However, we do not want to claim that the TANGO does not also recruit other, domain-general processes.
For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
From that perspective, gaze understanding could be seen as a particular case of vector-following that is learned and used in social interactions.
Future research could assess how much variation of the gaze understanding task is shared with a physical vector-following task.
In addition, computational cognitive models might prove helpful in defining children's behavior on a process-level and disentangling parameters that influence task performance (e.g., spatial acuity).

@@

Third, the children in our sample live in an industrialized, urban Central-European context. It is unclear how our results would generalize to different socio-cultural contexts. A limiting factor of our study is that we did not collect demographical information on a participant-level. Therefore, we could only provide a broader demographic description on a community-level. This is important to keep in mind when gauging the generalizability of our new measure.

@@

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and test-retest reliability.
The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person. Associations with social-environmental factors and language skills speak toward the validity of the task.
Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
The data sets and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
A demo version of the task is available at the following website (see Figure \@ref(fig:fig5)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
The code base and respective assets can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
These resources allow interested researchers to use, extend and adapt the task.

### 2023-05-12 stats/analysis.Rmd
incorporate reviews round 2

>>>>

```{r supplements_reli_byagegroup}
ggarrange(
  hedge_intCon_kids + facet_grid(~ ageInYears), 
  hedge_retest_kids + facet_grid(~ ageInYears),
  box_intCon_kids + facet_grid(~ ageInYears) + scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)), 
  box_retest_kids + facet_grid(~ ageInYears) + scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)), 
  nrow = 2, 
  ncol = 2, 
  labels = c("A", "B", "C", "D")
)

ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 8, height = 6)
```
